Fractional Types

### 2019-11-01 fracGC/p.tex
rephrase the bit about extracting a permutation from A <-> B in the language of lens.

Is the below a possible example?
\begin{verbatim}
Say we already have a permutation A <-> B
we can implement a permutation X <-> Z 
when there exists Y such that A/X = Y = B/Z

X -> X * Y * 1/Y 
  -> A * 1/Y
  -> B * 1/Y
  -> Y * Z * 1/Y
  -> Z
\end{verbatim}

>>>>

Is the below a possible example?
\begin{verbatim}
Say we already have a permutation A <-> B
we can implement a permutation X <-> Z 
when there exists Y such that A = X * Y = Z * Y = B

X -> X * Y * 1/Y 
  -> A * 1/Y
  -> B * 1/Y
  -> Y * Z * 1/Y
  -> Z * Y * 1/Y
  -> Z
\end{verbatim}
This basically says, in the language of Lens, that
when $A$ is isomorphic to $X \cross Y$ and
$B$ is isomorphic to $Z \cross Y$, then
$X$ is isomorphic to $Y$.

Another way to think of it: for all isomorphic
$A$ and $B$, whenever they can be factored with a
common complement ($Y$), then the ``other pieces''
(here $X$ and $Y$) are automatically isomorphic.
